Self Regulation Ontology Retest Data Report

### 2017-04-22 SRO_Report.Rmd
changed all dataframes to datatables

df
```

@@

Mean Spearman correlation and the number of variables for both the surveys and the tasks
```{r}
cor_df %>%
  group_by(task) %>%
  summarise(mean_spearman = mean(spearman),
            num_vars = n())
```

@@

- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
- Holt and Laury test-retest is the worst for *surveys*. But note that this is not a survey that has been studied extensively psychometrically like others. This is more similar to our tasks (one that is used more often by economists). In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.  
- Otherwise the lowest survey reliabilities are 0.5.
```{r}
cor_df %>%
  filter(task == 'survey') %>%
  select(dv, spearman) %>%
  arrange(-spearman)
```

@@

Median reliability and the number of variables for both the surveys and the tasks:
As seen with Spearman $\rho$'s as well the ICC's are higher for surveys.  
Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r}
icc_df %>%
  group_by(task) %>%
  summarise(median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

@@

#### Rank order of ICCs

```{r}
icc_df %>%
  filter(task == 'task') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-icc) %>%
  select(dv, -task, icc, eta_sq, sem, spearman)
```

```{r}
icc_df %>%
  filter(task == 'survey') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-icc) %>%
  select(dv, -task, icc, eta_sq, sem, spearman)
```

@@

#### Rank order of partial $\eta^2$

```{r}
icc_df %>%
  filter(task == 'task') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-eta_sq) %>%
  select(dv, -task, eta_sq, icc, sem, spearman)
```

```{r}
icc_df %>%
  filter(task == 'survey') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-eta_sq)%>%
  select(dv, -task, eta_sq, icc, sem, spearman)
```

@@

time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
time_effect_vars
```

@@

#### Rank order of SEMs

```{r}
icc_df %>%
  filter(task == 'task') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-sem) %>%
  select(dv, -task,  sem, eta_sq, icc, spearman)
```

```{r}
icc_df %>%
  filter(task == 'survey') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-sem)%>%
  select(dv, -task,  sem, eta_sq, icc, spearman)
```

@@

```{r}
icc_df %>%
  filter(icc>(-0.1), icc<0.1) %>%
  arrange(icc)
```

@@

tmp
```

@@

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  group_by(measure_type) %>%
  summarise(mean_icc = mean(icc),
            mean_spearman = mean(spearman),
            num_measures = n()) %>%
  arrange(-mean_icc, -mean_spearman)
```

@@

```{r warning=FALSE, message=FALSE}
tmp %>%
  group_by(label_1,label_2, label_3) %>%
  summarise(mean_icc = mean(icc),
            mean_spearman = mean(spearman),
            n_vars = n()) %>%
  arrange(-mean_icc, -mean_spearman)
```

This is what the distributions of look like

@@

```{r}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

>>>>

datatable(df)
```

@@

Mean Spearman correlation and the number of variables for both the surveys and the tasks
```{r}
datatable(cor_df %>%
  group_by(task) %>%
  summarise(mean_spearman = mean(spearman),
            num_vars = n()))
```

@@

- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
- Holt and Laury test-retest is the worst for *surveys*. But note that this is not a survey that has been studied extensively psychometrically like others. This is more similar to our tasks (one that is used more often by economists). In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.  
- Otherwise the lowest survey reliabilities are 0.5.
```{r}
datatable(cor_df %>%
  filter(task == 'survey') %>%
  select(dv, spearman) %>%
  arrange(-spearman))
```

@@

Median reliability and the number of variables for both the surveys and the tasks:
As seen with Spearman $\rho$'s as well the ICC's are higher for surveys.  
Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r}
datatable(icc_df %>%
  group_by(task) %>%
  summarise(median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n()))
```

#### Rank order of ICCs, partial $\eta^2$ and SEM

Note that these tables can be sorted for any of the columns.

```{r}
datatable(icc_df %>%
  filter(task == 'task') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-icc) %>%
  select(dv, -task, icc, eta_sq, sem, spearman))
```

```{r}
datatable(icc_df %>%
  filter(task == 'survey') %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  arrange(-icc) %>%
  select(dv, -task, icc, eta_sq, sem, spearman))
```

@@

@@

@@

time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
datatable(time_effect_vars)
```

@@

@@

```{r}
datatable(icc_df %>%
  filter(icc>(-0.1), icc<0.1) %>%
  arrange(icc))
```

@@

datatable(tmp)
```

@@

```{r warning=FALSE, message=FALSE}
datatable(measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  group_by(measure_type) %>%
  summarise(mean_icc = mean(icc),
            mean_spearman = mean(spearman),
            num_measures = n()) %>%
  arrange(-mean_icc, -mean_spearman))
```

@@

```{r warning=FALSE, message=FALSE}
datatable(tmp %>%
  group_by(label_1,label_2, label_3) %>%
  summarise(mean_icc = mean(icc),
            mean_spearman = mean(spearman),
            n_vars = n()) %>%
  arrange(-mean_icc, -mean_spearman))
```

This is what the distributions of look like. Note that there is one box in the difference columns for HDDM because this model only allows this to be different across conditions.

@@

```{r eval=FALSE, echo=FALSE}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}
